### 2022-12-15 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@1910093eefdd152d601a6c5d0ae3a79e33e933bc 🚀

Finally, our analytical and heuristic models can be used as alternative
null models of ecological networks to better understand and identify the
ecological processes driving food-web structure. Indeed, these
mechanisms can be better described when analyzing the deviation of
empirical data from MaxEnt predictions. A strong deviation would
indicate that ecological mechanisms not encodes in the statistical
constraints is at play for the system at hand. If deviations are
systematic, the maximum entropy model might need to be revised to
include appropriate ecological constraints. This revision process helps
us reflect on and identify what really constrains food-web structure.

@@

>>>>

Finally, our analytical and heuristic models can be used as alternative
null models of ecological networks to better understand and identify the
ecological processes driving food-web structure. Indeed, these
mechanisms can be better described when analysing the deviation of
empirical data from MaxEnt predictions. A strong deviation would
indicate that ecological mechanisms not encoded in the statistical
constraints are at play for the system at hand. If deviations are
systematic, the maximum entropy model might need to be revised to
include appropriate ecological constraints. This revision process helps
us reflect on and identify what really constrains food-web structure.
However, it is important to note here that tangible ecological
mechanisms cannot be directly inferred from statistical distributions
(Warren II, Costa, and Bradford 2022). Instead, by identifying the
constraints of a system and by analysing empirical deviations from
maximum entropy predictions, MaxEnt can only help us redirect research
efforts towards understanding the biological mechanisms behind these
constraints.

@@

\leavevmode\hypertarget{ref-WarrenII2022SeeSha}{}%
Warren II, Robert J., James T. Costa, and Mark A. Bradford. 2022.
{``Seeing Shapes in Clouds: The Fallacy of Deriving Ecological
Hypotheses from Statistical Distributions.''} \emph{Oikos} 2022 (11):
e09315. \url{https://doi.org/10.1111/oik.09315}.
